---
title: "Data analysis for tetrad discrimination tests"
format: 
  html:
    toc: true
    embed-resources: true
    from: markdown+emoji
server: shiny
---

```{r}
#| include: false

# load required libraries

library(tidyverse)
library(tidybayes)
library(bayesrules)

# initialize priors

prior_plots <- 
  tibble(certainty = c("sure they're different",
                     "not sure they're different",
                     "I really have no idea, but I hope they're different",
                     "I really have no idea, but I hope they're the same",
                     "not sure they're the same",
                     "sure they're the same"),
       proportion = c(1/3, 1/3, 1/3, 2/3, 2/3, 2/3),
       b_ratio = c(1/2, 1/2, 1/2, 2, 2, 2),
       a = c(6, 4, 2, 1, 2, 3),
       b = b_ratio * a) |>
  mutate(prior_plot = map2(a, b, plot_beta),
         title = map2_chr(a, b, \(x, y) str_c("beta(", x, ", ", y, ")"))) |>
  mutate(prior_plot = map2(prior_plot, title, \(x, y) x + ggtitle(label = y))) |>
  mutate(prior_plot = map2(prior_plot, certainty, \(x, y) x + labs(subtitle = y)))

```


To use this part of the toolkit, you will need the results of your tetrad test.  Specifically, you will need:

*  The number of subjects who participated, which we can call $N$.  
*  The number of subjects *who got the right answer*, which we can call $x$.  By necessity, $x≤N$. 
*  Your prior intuition for how easy it would be for panelists to tell the difference between the samples.  

We'll also collect the names of products A and B so that we can generate some nice reports that don't just say "A" and "B" on them.  We won't keep this information for anything, but if you're uncomfortable using identifying information that's fine--you can use made up info, or even just use "A" and "B".

Once you've got those, we're ready to get analyzing!

# What you'll get from this data analysis

Before we get to the analysis, a quick, intuitive explanation.  Above, we talked about two important numbers: $x$ and $N$.  In fact, the proportion of correct answers, $x/N$ is the key quantity we're interested in here.  Specifically, we're interested in what insight $x/N$ gives us into the true proportion of people who will notice a difference in your two products, A and B, which we'll call $\pi$.  Because $\pi$ is also a proportion, $0≤\pi≤1$, but we will present results in terms of both $\pi$ and in terms of the number of people in 100 who would notice a difference.

Intuitively, if $\pi$ is closer to $1$, then most people will notice a difference.  If $\pi$ is closer to $0$, then very few people will.  By giving some worst- and best-case outcomes, we'll tell you what you should expect to see, based on your prior intuition and your actual data, if you brought your products to market.

# Data analysis for tetrad tests

Great!  With that understanding, we can analyze your data. 

```{r}

```

